Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Add section on stability of the program

>>>>

    \subsection{Stability of the program}
        An interesting thing would be to model large systems of many particles
        and with large hard sphere radii. Unfortunately, due to the shape of the
        single particle functions this turns out to be quite tricky. As the
        single particle function consists of a sum squared positions from a
        given center, many particles and/or spread out systems will yield a
        large sum. This means that the Slater permanent grows smaller and
        smaller making it much harder to keep the system confined. By lowering
        the frequency and thus lowering the minimum $\alpha$ we can remedy some
        of this behaviour.
